Chemistry of the Orphan Stream I: Identifying Stream Candidates with Low Resolution Spectroscopy

### 2012-09-03 2012-oss-mrs/draft-oss-mrs.tex
Made most corrections to GDC comments and suggestions

\begin{abstract}
We present coordinates and properties of K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Australian Astronomical Telescope. With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members. Our data indicates an overall stream metallicity of [Fe/H] $= -1.74 \pm 0.05$ which is more metal-rich than previously found and unbiased by spectral type. We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{helio} \sim 218$\,km s$^{-1}$. We highlight members for high resolution spectroscopic follow-up.
\end{abstract}

@@

The Milky Way stellar halo has been partly formed through the accretion of smaller satellites. As smaller satellites infall onto the Milky Way, tidal forces disrupt the satellite. Stars which were once gravitationally bound to the satellite are left behind in a stream of stars. Stream members have kinematics which are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Milky Way. The level of accreted substructure in the Milky Way has only recently become apparent through multi-band photometric surveys like the Sloan Digital Sky Survey (SDSS). The more prominent of the detectable substructures, like Sagittarius, have been well-studied. One of the more prominent \-- yet less studied \-- substructures is that of the Orphan Stream.

The Orphan Stream was independently detected by both \citet{Grillmair;Dionatos_2006} and \citet{Belokurov;et-al_2006}, and is unique from other substructures in the halo. The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2^\circ$ and as the name suggests, the parent largely remains a mystery. The stream extends past the celestial equator \-- outside the SDSS footprint \-- and is not detectable through bright southern surveys like SuperCOSMOS [citation needed]. Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker;et-al_2006, Fellhaur;et-al_2007,Jin;Lynden_Bell_2007,Sales;et-al_2008}. In contrast, there has been relatively limited observational work on the Orphan Stream other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}. This is largely to be expected given the absence of multi-band photometry in the southern sky, the difficulty in reliably separating Orphan Stream members from halo stars and the low luminosity of stream members. It is unlikely the full extent of the Orphan Stream will be detected until the SkyMapper telescope surveys this region \citep{Keller;et-al_2007}.

@@

In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream. Using our selection method we have published the locations of seven highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up. In the following section of this letter we outline our initial photometric target selection. In section \S\ref{sec:target-selection} we outline our target selection and section \S\ref{sec:observations} describes the low resolution observations. The data analysis, including stream identification, is described in \S\ref{sec:analysis}. In \S\ref{sec:conclusions} we discuss our conclusions, predictions, and necessary future work necessary on this topic.

@@

We have targeted K giant members of the Orphan Stream in order to investigate their detailed chemistry. Because K-giants are difficult to unambiguously detect from photometry alone, low resolution spectroscopy is required to estimate stellar parameters and determine radial velocities. The Orphan Stream has a low spatial over-density on the order of $\sim10\%$ [citation needed], which also makes it difficult to separate stream members from halo stars. However, there is a well described distance gradient along the stream \citep{Belokurov;et-al_2007, Newberg;et-al_2010} which provides an indication on where we should focus our spectroscopic efforts.

@@

Given our colour selection we expect to recover giants and dwarf contaminants. At a given temperature, K dwarfs exhibit a infrared excess relative to giants which allows a clean selection of giants \citep{Bessell;Brett_1988}. However, given the apparent magnitude of the Orphan Stream in this region ($g \sim 18$), no 2MASS infrared photometry is available. Thus we expect our sample to be contaminated by foreground dwarfs to some extent.

@@

Observations took place on the Australian Astronomical Telescope using the AAOmega spectrograph in April 2009. AAOmega is a fibre-fed, dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 400 (science and sky) targets across a $2^\circ$ field of view. We used the 5700\,{\AA} dichroic in combination with the 1000I grating in the red arm, and the 580V grating in the blue arm. This provides a spectral coverage between $800 \leq \lambda \leq 950$\,nm in the red at $\mathcal{R} \approx 4400$, and between $370 \leq \lambda \leq 580$\,nm with a lower resolving power of $\mathcal{R} \approx 1300$.

The data were reduced using the supplied \textsc{2DFDR} reduction pipeline \footnote{http://www.aao.gov.au/2df/aaomega/aaomega\_2dfdr.html}. After flat-fielding, throughput calibration for each fibre was achieved using the intensity of skylines in each fibre. The median flux of dedicated sky fibres was taken for sky subtraction, and wavelength calibration was performed using arc lamp exposures between science frames. Three thirty minute science exposures were median combined to assist with cosmic ray removal. The median S/N obtained in the red arm for our fields is modest at 35\,px$^{-1}$. With the presence of strong Ca \textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg;et-al_2010}. Our spectral region also includes gravity-sensitive magnesium lines: Mg I at 8807\,{\AA}, and the Mg Ib 3$p$-4$s$ triplet lines. As we demonstrate in the next section, these lines are sufficient to discriminate dwarfs and giants even with weak signal.

@@

In this region \citet{Newberg;et-al_2010} found the Orphan Stream to have $V_{\textsc{gsr}} = 110$ km s$^{-1}$ from BHB stars, approximately $105$\,km s$^{-1}$ on our scale. We have nominated a relatively wide kinematic selection region between $75 \leq V_{\textsc{gsr}} \leq 135$ km s$^{-1}$, which yields 25 Orphan Stream candidates. The typical uncertainty in our kinematics is $\pm{}3.5$\,km s$^{-1}$, although for our fainter targets this quickly increases to $\sim10$ km s$^{-1}$.

@@

We have measured the equivalent widths of the gravity-sensitive Mg I line at 8807 \AA{} to distinguish dwarfs from giants. At a given temperature (or $g \-- r$) and metallicity, giant stars present narrow Mg I absorption lines than their dwarf contaminants. Given our target selection, our sample is likely to contain many more dwarfs than giants. In four cases no Mg I 8807 \AA{} line was apparent, so an upper limit was estimated based on the S/N. In these cases the candidate was considered a ``non-dwarf" because we cannot exclusively rule out a metal-poor sub-giant with this criterion alone. For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not. Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS $g \-- r$ de-reddened\footnote{All magnitudes presented in this paper are de-reddened}, illustrating the dominant upper dwarf branch we wish to exclude. The adopted dwarf/giant separation line is shown. Admittedly this selection criterion appears extremely inclusive of dwarfs, but we are allowing multiple inclusive cuts and taking the union of these selections to identify Orphan Stream giants.

@@

It is worth noting that we initially performed this analysis using the total equivalent width of the Mg\,\textsc{I}b triplet near 5175\,{\AA}. As expected, this region has a consistently lower S/N than the Mg\,\textsc{I} line at 8807\,{\AA}. However, the separation between giants and dwarfs was arguably more distinguished when using the Mg I b triplet equivalent width instead of using the $\lambda{}8807$ line. In either case, both analyses were entirely consistent with each other: the same candidate selection was found using both techniques. However, given the poorer signal at the Mg\,\textsc{I}b triplet, we were forced to adopt many more upper limits than when using the 8807{\AA} line. Because we classify all upper limits as being ``non-dwarfs" (i.e. potential OSS giants), we deduced a slightly larger candidate sample for the Mg\,\textsc{I}b analysis, which was primarily populated by upper limits. In conclusion, we found the Mg\,\textsc{I} line at 8807 appeared to be a more consistent dwarf discriminant given our weak S/N \--- particularly for our fainter stars \--- and thus we have used the 8807{\AA} Mg \textsc{I} selection throughout the rest of our analysis.

Our dwarf/giant separation line in Figure \ref{fig:ew-mg} yields 425 potential giants. This fraction of giants ($\sim{}44\%$) is much larger than what would be expected given our selection criterion (e.g. see \citet{Casey;et-al_2012a}). Hence, our gravity criterion is extremely inclusive and susceptible to dwarf contamination. Upon taking the union of our kinematic and gravity selections, we deduce eighteen stars that appear likely Orphan Stream K giants.

@@

We have measured the equivalent widths of the Ca\,\textsc{II} near-infrared triplet lines for stars which meet our kinematic and surface gravity criteria. After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication for the metallicity of a RGB star \citep{Amandroff;Da_Costa_1991}. We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_0$ = 17.1 \citep{Newberg;et-al_2010}. Strictly speaking, the Ca\,\textsc{II}-[Fe/H] relationship is only valid for stars brighter than the horizontal branch, although the situation only becomes dire at $g \-- g_{HB} \sim +1$ [citation needed]. Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities. Stars fainted than $g_0$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}-[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.

@@

Figure \ref{fig:cmd} illustrates all eighteen candidates which meet both our kinematic and surface gravity criterion. Candidates are coloured by their metallicity deduced from the Ca\,\textsc{II} triplet. There are four candidates above $g_0 \sim 17.1$ which are within our valid luminosity range. Two of these objects at $g \-- r \sim 0.57$ are slightly metal-rich than expected for the stream, and are excluded from membership. There appears to be an extremely metal-poor star in this sample with an estimated $[\mbox{Fe/H}] = -2.70$ which may be associated with the Orphan Stream. The likely parent system of the Orphan Stream is a Milky Way dwarf spheroidal \citep{Belokurov;et-al_2007, Sales;et-al_2008}, which are known to have a wide metallicity distribution function [citation needed?], including an over-represented population of extremely metal poor stars \citep{Frebel;et-al_2010, Kirby;et-al_2010}. Thus, we keep this extremely metal-poor star as a potential stream member for follow-up chemical analysis. 
% speak about OSS 1?

\citet{Newberg;et-al_2010} found the median Orphan Stream metallicity to be [Fe/H] $= -2.1$ from BHB stars, and a distance of $21.4 \pm 1.0$\,kpc in this region. In Figure \ref{fig:cmd} we have overlaid 10 Gyr old isochrones from \citet{Girardi;et-al_2008} with metallicities of [Fe/H] $= -2.0$ and $-1.5$ at a distance of $21.4$ kpc \citep{Newberg;et-al_2010}. Four of our most probable Orphan Stream members fall between these isochrones. Assuming the three highly probable members outside our valid luminosity range are over-predicted by $\sim+0.1$ dex [citation needed], when combining our four Orphan Stream members we yield a stream metallicity of $[\mbox{Fe/H}] = -1.74 \pm 0.05$. This is slightly more metal-rich than the $[\mbox{Fe/H}] =-2.1$ found by \citet{Newberg;et-al_2010} from BHB stars. This is to be expected as BHB stars are intrinsically representative of an older, more metal-poor population.

@@

The K giants presented here can provide great insight into the chemistry, and history of the Orphan Stream. High resolution spectroscopic observations have been taken for our most highly probable members and a detailed chemical analysis will be presented in an accompanying paper (Casey et al. 2012c, in preparation). Detailed chemical abundances can help determine both the nature of the host system, and allow us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents. However at least for the moment, the Orphan Stream remains appropriately named.

\section{Acknowledgements}
ARC acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship, which has facilitated his research at MIT. SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Program DP0878137.

>>>>

\begin{abstract}
We present coordinates and properties of candidate K giant members in the Orphan Stream, which have been identified from low resolution spectroscopic data taken with AAOmega on the Australian Astronomical Telescope. With modest S/N and independent cuts in photometry, kinematics, gravity and metallicity we yield self-consistent, highly probable stream members. Our data indicates an overall stream metallicity of [Fe/H] $= -1.74 \pm 0.05$ which is more metal-rich than previously found and unbiased by spectral type. We find a revised stream distance of 24 kpc near the celestial equator, and our kinematic signature peaks at $V_{helio} \sim 218$\,km s$^{-1}$. We highlight likely members for high resolution spectroscopic follow-up.
\end{abstract}

@@

The Milky Way stellar halo has partly formed through the accretion of satellites which are disrupted by tidal forces as they fall into the Milky Way's potential. Stars which were once gravitationally bound to the satellite are left behind in a stream of stars. Stream kinematics are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Milky Way. The level of accreted substructure in the Milky Way has only recently become apparent through multi-band photometric surveys like the Sloan Digital Sky Survey (SDSS). The more prominent of the detectable substructures, like Sagittarius, have been well-studied. One of the more prominent \-- yet less studied \-- substructures is that of the Orphan Stream.

The Orphan Stream was independently detected by both \citet{Grillmair;Dionatos_2006} and \citet{Belokurov;et-al_2006}, and is distinct from other substructures in the halo. The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim2^\circ$ and as the name suggests, the parent object largely remains a mystery. The stream extends past the celestial equator \-- outside the SDSS footprint \-- but is not detected in existing southern surveys \citep{Newberg;et-al_2010}. Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker;et-al_2006, Fellhaur;et-al_2007,Jin;Lynden_Bell_2007,Sales;et-al_2008}. In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair;Dionatos_2006, Belokurov;et-al_2006, Belokurov;et-al_2007} and the work of \citet{Newberg;et-al_2010}. This is largely to be expected given the absence of multi-band photometry in the southern sky, the difficulty in reliably separating Orphan Stream members from halo stars and the low luminosity of stream members. It is unlikely the full extent of the Orphan Stream will be detected until the SkyMapper telescope surveys this region \citep{Keller;et-al_2007}.

@@

In this letter we present a detailed, self-consistent analysis to identify K giant members of the Orphan Stream. Using our selection method we have catalogued the locations of seven highly probable Orphan Stream candidates, all worthy of high resolution spectroscopic follow up. In the following section we outline our photometric target selection. In Section \S\ref{sec:observations} we describe the low resolution spectroscopic observations. The data analysis, including stream identification, is discussed in \S\ref{sec:analysis} and in \S\ref{conclusions} the conclusions, predictions and future work are presented.

@@

We have targeted K giant members of the Orphan Stream in order to investigate their detailed chemistry. Because K-giants are difficult to unambiguously detect from photometry alone, low resolution spectroscopy is required to estimate stellar parameters and determine radial velocities. The Orphan Stream has a low spatial over-density on the order of $\sim10\%$ [citation needed], which makes it difficult to separate stream members from halo stars. However, there is a well described distance gradient along the stream \citep{Belokurov;et-al_2007, Newberg;et-al_2010} which provides an indication on where we should focus our spectroscopic efforts.

@@

Given our colour selection we expect to recover giants and dwarf contaminants. The lack of 2MASS photometry for the selected stars means we cannot use the $(J-H, H-K)$ diagram to aid the separation of candidate giants from contaminating dwarfs.

@@

Observations took place on the Australian Astronomical Telescope using the AAOmega spectrograph in April 2009. AAOmega is a fibre-fed, dual beam multi-object spectrograph which is capable of simultaneously observing spectra of 400 (science and sky) targets across a $2^\circ$ field of view. We used the 5700\,{\AA} dichroic in combination with the 1000I grating in the red arm, and the 580V grating in the blue arm. This provides a spectral coverage between $800 \leq \lambda \leq 950$\,nm in the red at $\mathcal{R} \approx 4400$, and between $370 \leq \lambda \leq 580$\,nm with a lower resolving power of $\mathcal{R} \approx 1300$ in the blue.

The data were reduced using the standard \textsc{2DFDR} reduction pipeline \footnote{http://www.aao.gov.au/2df/aaomega/aaomega\_2dfdr.html}. After flat-fielding, throughput calibration for each fibre was achieved using the intensity of skylines in each fibre. The median flux of dedicated sky fibres was taken for sky subtraction, and wavelength calibration was performed using arc lamp exposures between science frames. Three thirty minute science exposures were median combined to assist with cosmic ray removal. The median S/N obtained in the red arm for our fields is modest at 35\,px$^{-1}$. With the presence of strong Ca \textsc{II} triplet lines in the red arm we are able to ascertain reliable radial velocities and reasonable estimates on overall metallicity \citep[][and references therein]{Starkenburg;et-al_2010}. Our spectral region also includes gravity-sensitive magnesium lines: Mg I at 8807\,{\AA}, and the Mg I\,b 3$p$-4$s$ triplet lines at $\sim$5178\,{\AA}. As we demonstrate in the next section, these lines are sufficient to discriminate dwarfs and giants even with weak signal.

@@

In this region \citet{Newberg;et-al_2010} found the Orphan Stream to have $V_{\textsc{gsr}} = 110$ km s$^{-1}$ from BHB stars, approximately $105$\,km s$^{-1}$ on our scale. To isolate potential Orphan Stream members we have nominated a relatively wide kinematic selection region between $75 \leq V_{\textsc{gsr}} \leq 135$ km s$^{-1}$, which yields 25 Orphan Stream candidates. The typical uncertainty in our kinematics is $\pm{}3.5$\,km s$^{-1}$, although for our fainter targets this quickly increases to $\sim10$ km s$^{-1}$.

@@

We have measured the equivalent widths of the gravity-sensitive Mg I line at 8807 \AA{} to distinguish dwarfs from giants \citep{Battaglia;Starkenburg_2012}. At a given temperature (or $g \-- r$) and metallicity, giant stars present narrow Mg I absorption lines than their dwarf contaminants. Given our target selection, our sample is likely to contain many more dwarfs than giants. In four cases no Mg I 8807 \AA{} line was apparent, so an upper limit was estimated based on the S/N. In these cases the candidate was considered a ``non-dwarf" because we cannot exclusively rule out a metal-poor sub-giant with this criterion alone. For these purposes we are only looking for a simple indication as to whether a star is likely a dwarf or not. Figure \ref{fig:ew-mg} illustrates the trend with EW$_{\lambda8807}$ against SDSS $g \-- r$ de-reddened\footnote{All magnitudes presented in this paper are de-reddened}, illustrating the dominant upper dwarf branch we wish to exclude. The adopted dwarf/giant separation line is shown. Admittedly this selection criterion is not particularly strict, but we are allowing multiple inclusive cuts and taking the intersection of these criteria to identify Orphan Stream giants.

@@

This analysis was also performed using the total equivalent width of the Mg\,\textsc{I}\,b triplet lines. Both analyses were entirely consistent with each other: essentially the same candidate selection was found using both techniques. However, given slightly poorer signal at the Mg\,\textsc{I}\,b triplet, we were forced to adopt many more upper limits than when using the 8807{\AA} line. Because we classify all upper limits as being ``non-dwarfs" (i.e. potential OSS giants), we deduced a slightly larger candidate sample for the Mg\,\textsc{I}\,b analysis, which was primarily populated by upper limits. In conclusion, we found the Mg\,\textsc{I} line at 8807 appeared to be a more consistent dwarf discriminant given our weak S/N \--- particularly for our fainter stars \--- and thus we have used the 8807{\AA} Mg \textsc{I} selection throughout the rest of our analysis.

Our dwarf/giant separation line in Figure \ref{fig:ew-mg} yields 425 potential giants. This fraction of giants ($\sim{}44\%$) is much larger than what would be expected given our selection criterion (e.g. see \citet{Casey;et-al_2012a}). Hence, our gravity criterion is extremely inclusive and susceptible to dwarf contamination. Upon taking the intersection of our kinematic and gravity selections, we deduce eighteen stars that appear likely Orphan Stream K giants.

@@

We have measured the equivalent widths of the Ca\,\textsc{II} near-infrared triplet lines for stars which meet our kinematic and surface gravity criteria. After correcting for luminosity, the equivalent width of the Ca\,\textsc{II} triplet lines provide a good indication for the metallicity of a RGB star \citep{Amandroff;Da_Costa_1991}. We have employed the \citet{Starkenburg;et-al_2010} relationship and corrected for luminosity in $g$ against the horizontal branch magnitude at $g_0$ = 17.1 \citep{Newberg;et-al_2010}. Strictly speaking, the Ca\,\textsc{II}-[Fe/H] calibation is only valid for stars brighter than the horizontal branch, although the relationship only becomes significantly inappropriate near $g \-- g_{HB} \sim +1$ \citep{Savine;et-al_2012}. Many of our candidates are fainter than this valid luminosity range, and therefore they should not be excluded solely because of their derived metallicities. Stars fainted than $g_0$ will have slightly lower metallicities than predicted by our Ca\,\textsc{II}-[Fe/H] relationship, and for these stars we will only use metallicities to assign a relative qualitative likelihood for stream membership.

@@

Figure \ref{fig:cmd} illustrates all eighteen candidates which meet both our kinematic and surface gravity criterion. Candidates are coloured by their metallicity deduced from the Ca\,\textsc{II} triplet. There are four candidates above $g_0 \sim 17.1$ which are within our valid luminosity range. One of these objects at $(g \-- r, g) \sim (0.57, 17)$ is +0.64\,dex more metal-rich than expected for the stream, and is excluded from membership. Another is only +0.21\,dex more metal-rich and sits at (0.57, 16.1), but it's position relative to the isochrone is inconsistent with our inferred metallicity. There appears to be an extremely metal-poor star in this sample with an estimated $[\mbox{Fe/H}] = -2.70$ which may be associated with the Orphan Stream. The likely parent system of the Orphan Stream is a Milky Way dwarf spheroidal \citep{Belokurov;et-al_2007, Sales;et-al_2008}, which are known to have a wide metallicity distribution function \citep{Tafelmayer;et-al_2010, Tolstoy;et-al_2009}, including an over-represented population of extremely metal poor stars \citep{Frebel;et-al_2010, Kirby;et-al_2010}. Thus, we keep this extremely metal-poor star as a potential stream member for follow-up chemical analysis. 
% speak about OSS 1?

\citet{Newberg;et-al_2010} found the median Orphan Stream metallicity to be [Fe/H] $= -2.1$ from BHB stars, and a distance of $21.4 \pm 1.0$\,kpc in this region. In Figure \ref{fig:cmd} we have overlaid 10 Gyr old isochrones from \citet{Girardi;et-al_2008} with metallicities of [Fe/H] $= -2.0$ and $-1.5$ at a distance of $21.4$ kpc \citep{Newberg;et-al_2010}. Four of our most probable Orphan Stream members fall between these isochrones. Assuming the three highly probable members outside our valid luminosity range are over-predicted by $\sim+0.1$ dex [citation needed], when combining our four Orphan Stream members we yield a stream metallicity of $[\mbox{Fe/H}] = -1.74 \pm 0.05$. This is slightly more metal-rich than the $[\mbox{Fe/H}] =-2.1$ found by \citet{Newberg;et-al_2010} from BHB stars.

@@

The K giants presented here can provide great insight into the chemistry, and history of the Orphan Stream. High resolution spectroscopic observations have been taken for our most highly probable members and a detailed chemical analysis will be presented in a forthcoming paper (Casey et al. 2012c, in preparation). Detailed chemical abundances can help determine both the nature of the host system, and allow us to compare peculiar chemical signatures with those of the known Milky Way satellites in order to associate likely parents. However at least for the moment, the Orphan Stream remains appropriately named.

\acknowledgements
ARC acknowledges the financial support through the Australian Research Council Laureate Fellowship 0992131, and from the Australian Prime Minister's Endeavour Award Research Fellowship, which has facilitated his research at MIT. SK and GDaC acknowledge the financial support from the Australian Research Council through Discovery Programs DP0878137 and DP120101237.
